Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-10 ms/SI.Rmd
Combine SES and spatial results in plan

loadd(list = c(
  "comm_scaled_list_0.1",
  "comm_scaled_list_0.2",
  "comm_scaled_list_0.3",
  "comm_scaled_list_0.4",
  "richness_by_res",
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny",
  "species_motifs_ferns",
  "species_motifs_ferns_combined",
  "traits_nmds",
  "ppgi"
),
cache = ja_fern_cache)

@@

```{r plot-prep}
# Combine bioregion results, biodiversity metrics, and shape data into single dataframe
tax_regions_data <- regions_taxonomy %>%
  mutate(taxonomic_cluster = as.factor(cluster) %>% fct_infreq %>% as.numeric %>% as.factor) %>%
  select(grids, taxonomic_cluster)

phy_regions_data <- regions_phylogeny %>%
  mutate(phylo_cluster = as.factor(cluster) %>% fct_infreq %>% as.numeric %>% as.factor) %>%
  select(grids, phylo_cluster)

ses_div_ferns_spatial <-
  shape_ferns %>%
  left_join(ses_phy_ferns, by = c(grids = "site")) %>%
  left_join(ses_traits_ferns, by = c(grids = "site")) %>%
  left_join(tax_regions_data, by = "grids") %>%
  left_join(phy_regions_data, by = "grids")

# - same for endemic species
ses_div_ferns_endemic_spatial <-
shape_ferns %>%
  left_join(ses_phy_ferns_endemic, by = c(grids = "site"))

# Define ggplot2 theme for maps
map_theme <- theme(
    panel.grid.major = element_line(color = "grey95", size = 0.1),
    panel.background = element_rect(fill = "grey60"),
    axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.7)
  )

>>>>

loadd(list = c(
  "comm_scaled_list_0.1",
  "comm_scaled_list_0.2",
  "comm_scaled_list_0.3",
  "comm_scaled_list_0.4",
  "occ_point_data_ferns",
  "ses_div_ferns_spatial",
  "ses_div_ferns_endemic_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "traits_nmds",
  "ppgi"
),
cache = ja_fern_cache)

@@

```{r plot-prep}
# Define ggplot2 theme for maps
map_theme <- theme(
    panel.grid.major = element_line(color = "grey95", size = 0.1),
    panel.background = element_rect(fill = "grey60"),
    axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.7)
  )

### 2020-07-10 ms/manuscript.Rmd
Combine SES and spatial results in plan

loadd(list = c(
  "occ_point_data_ferns",
  "occ_point_data_ferns_unfiltered",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny"
),
cache = ja_fern_cache)

@@

```{r plot-prep}
tax_regions_data <- regions_taxonomy %>%
  mutate(taxonomic_cluster = as.factor(cluster) %>% fct_infreq %>% as.numeric %>% as.factor) %>%
  select(grids, taxonomic_cluster)

phy_regions_data <- regions_phylogeny %>%
  mutate(phylo_cluster = as.factor(cluster) %>% fct_infreq %>% as.numeric %>% as.factor) %>%
  select(grids, phylo_cluster)

ses_div_ferns_spatial <-
  shape_ferns %>%
  left_join(ses_phy_ferns, by = c(grids = "site")) %>%
  left_join(ses_traits_ferns, by = c(grids = "site")) %>%
  left_join(tax_regions_data, by = "grids") %>%
  left_join(phy_regions_data, by = "grids")

ses_div_ferns_endemic_spatial <-
shape_ferns %>%
  left_join(ses_phy_ferns_endemic, by = c(grids = "site"))

>>>>

loadd(list = c(
  "occ_point_data_ferns",
  "occ_point_data_ferns_unfiltered",
  "ses_div_ferns_spatial",
  "k_taxonomy",
  "k_phylogeny"
),
cache = ja_fern_cache)

@@

```{r plot-prep}
# Change cluster to factor
ses_div_ferns_spatial <- ses_div_ferns_spatial %>%
  mutate(taxonomic_cluster = as.factor(taxonomic_cluster) %>% fct_infreq %>% as.numeric %>% as.factor) %>%
  mutate(phylo_cluster = as.factor(phylo_cluster) %>% fct_infreq %>% as.numeric %>% as.factor)
